Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/experiments.tex

\paragraph{Qualitative experiments: Visualizing policies and values.}
To provide qualitative results, and check robustness to time
discretization both in terms of raw return results and in terms
of convergence of the approximate value function and policies, we first provide results on the simple pendulum environment
from the OpenAI Gym classic control suite.  Its state space is of
dimension $2$. We visualize both the learnt value and policy functions by
plotting, for each point of the phase diagram $(\theta, \dot{\theta})$,
its value and policy. The results are presented in
Fig.~\ref{fig:pend} for the policy function and in Fig.\TODO{ref} in Supplementary \TODO{ref} for the value function.

We observe the learnt policy at several instants in physical time (or normalized epochs) during training, for various time discretizations $\deltat$, for both DAU and DDPG. With DAU, the agent's policy quickly converges for every time discretization without specific hyperparameter tuning. On the contrary, with DDPG, the agent is only able to learn for the two highest time discretization, and learning gets harder as $\deltat$ decreases.

>>>>

\paragraph{Qualitative experiments: Visualizing policies and values.}
To provide qualitative results, and check robustness to time
discretization both in terms of raw return results and in terms
of convergence of the approximate value function and policies, we first provide results on the simple pendulum environment
from the OpenAI Gym classic control suite.  Its state space is of
dimension $2$. We visualize both the learnt value and policy functions by
plotting, for each point of the phase diagram $(\theta, \dot{\theta})$,
its value and policy. The results are presented in
Fig.~\ref{fig:pend} (policy function) and in Fig.\TODO{ref} in
Supplementary \TODO{ref} (value function).

We plot the learnt policy at several instants in physical time (or
normalized epochs) during training, for various time discretizations
$\deltat$, for both DAU and DDPG. With DAU, the agent's policy quickly
converges for every time discretization without specific hyperparameter
tuning. On the contrary, with DDPG, the agent is only able to learn for
the two largest time discretizations; DDPG learning gets harder as $\deltat$ decreases.
